\clearpage

\renewcommand{\bibname}{\xiaoyi\bf\vspace{5pt} References}
\addcontentsline{toc}{chapter}{References}
\setstretch{1.25}

\begin{thebibliography}{99}
    \setlength{\itemindent}{-5pt}
    \bibitem{1} ENGEL P A.  Impact Wear of Materials[M]. 2nd ed. New York: Elsevier, 1986. (Published books: should give authors, title of the book, edition, publisher, publish year and the page cited if applicable.)
    \bibitem{2}	Hao, Z., AghaKouchak, A., Nakhjiri, N. \& Farahmand, A. Global Integrated Drought Monitoring and Prediction System (GIDMaPS) data sets. figshare http://dx.doi.org/10.6084/m9.figshare.853801 (2014). (research datasets: Research datasets may be cited in the reference list if they have been assigned digital object identifiers (DOIs) and include authors, title, publisher (repository name), identifier (DOI expressed as a URL). )
    \bibitem{3}	Babichev, S. A., Ries, J. \& Lvovsky, A. I. Quantum scissors: teleportation of single-mode optical states by means of a nonlocal single photon. Preprint at http://arXiv.org/quant-ph/0208066 (2002). (Recognized preprints may be cited in the reference list.)
    \bibitem{4}	Yu, X., Li, C., Wang, Z., Xu, Y., Shao, S., Shao, F., Wang, H., \& Liu, J. Neutrophils in cancer: dual roles through intercellular interactions. Oncogene, 2024, 43(11), 1-15 (published journal papers or conference abstracts: should give authors, article title and journal name as above, followed by URL in full - or DOI if known - and the year of publication in parentheses.)
    \bibitem{5}	Lu, Q. et. al. www.bing.com (Websites: should give authors if known, title of cited page, URL in full, and year of posting in parentheses.)
    \bibitem{6}	Hilderbran, S., Weissleder, R., and Shao, F., Monofunctional carbocyanine dyes for in vivo and in vitro imaging, US Patent No. WO 2010054330, May, 2010 (numbered patents: should give authors, patent title and patent number and country)
    \bibitem{7} Wang Y., Zhang Q., Qin M., et.al Knowledge-aware Reinforced Language Models for Protein Directed Evolution Proceedings of the 41st International Conference on Machine Learning, PMLR 235:52260-52273, 2024. (conference paper: should give authors, Title of contribution [Paper presentation]. conference Name, Location, Year, Date. DOI or URL)
\end{thebibliography}
\doublespacing